```{r echo = FALSE}
knitr::read_chunk("./analyse.r")
knitr::opts_chunk$set(message = FALSE)
```

# Death row
Analysis of death row inmates' final statements before execution. Data scraped
from Texas Department of Criminal Justice website.

## General statistics

### Executions per year

```{r executions-per-year, echo = FALSE}
```

### Race distribution by year

```{r race-distribution-by-year, echo = FALSE}
```

### Average age at execution by year

```{r average-age-by-year, echo = FALSE}
```

### Average age at execution by race

```{r average-age-by-race, echo = FALSE}
```

## Word clouds

### Most frequent words

```{r frequent-words, echo = FALSE}
```

### Most frequent phrases (trigrams)

```{r frequent-phrases, echo = FALSE, warning = FALSE}
```

## Sentiment analysis

```{r echo = FALSE}
sentiments <- data %>%
  mutate(sentiment = sentiment_by(statement)$ave_sentiment) %>%
  select(c("statement", "sentiment")) %>%
  filter(!str_detect(statement, "offender declined|not found")) %>%
  filter(nchar(statement) > 100) %>%
  arrange(sentiment)
```

#### Example of statements with negative sentiment

```{r echo = FALSE, results = "asis"}
pprint <- function(x) {
  paste("* ", x[1], "\n", "*Score: ", x[2], "*\n", sep = "")
}

writeLines(apply(head(sentiments, 10), 1, pprint))
```

#### Example of statements with positive sentiment

```{r echo = FALSE, results = "asis"}
writeLines(apply(tail(sentiments, 10), 1, pprint))
```

### Sentiment by age

```{r sentiment-by-age, echo = FALSE}
```

### Sentiment by race
```{r sentiment-by-race, echo = FALSE}
```
